---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cureplots

<!-- badges: start -->

[![Codecov test coverage](https://codecov.io/gh/gbasulto/cureplots/branch/master/graph/badge.svg)](https://app.codecov.io/gh/gbasulto/cureplots?branch=master)

<!-- badges: end -->

Cumulative residual (CURE) plots assess the goodness-of-fit of a covariate in a generalized linear regression model, usually a negative binomial regression or a Poisson regression. The package `cureplots` produces CURE plots for the requested variables produced with [`ggplot2`](https://ggplot2.tidyverse.org/) or a table to easily produce a customized plot with the desired package.

## Installation

Install the latest CRAN version with

``` r
install.packages("cureplots")
```

You can install the development version of `cureplots` from [GitHub](https://github.com/) with the following:

``` r
# install.packages("devtools")
devtools::install_github("gbasulto/cureplots")
```

## Functions and Data

| Name                       | Purpose                                                                                                                                                                                                                                                       |
|--------------------------|----------------------------------------------|
| `calculate_cure_dataframe` | Calculate CURE dataframe. Useful to produce customized CURE plots or CURE plots with variables not included in the model or transformations of variables that were included in the model (e.g., CURE plot for AADT when log(AADT) was included in the model). |
| `cure_plot`                | Produce default CURE plot by either providing model and variable to plot or an output from `calculate_cure_dataframe` function.                                                                                                                               |
| `resample_residuals`       | Resample cumulative residuals to overlay to CURE plots and better interpret results.                                                                                                                                                                          |
| `washington_roads`         | Curated dataframe of crashes in Washington roads.                                                                                                                                                                                                             |

: Functions in `cureplots`

## Basic Example

The example below shows

-   How to produce a cure plot directly from the model object and
-   How to produce the table to customize a plot.

A Poisson GLM model is adjusted to simulated data using the package `glm`. The functions also work with the `gam` package.

```{r example}
library(cureplots)

## basic example

set.seed(2000)

## Define parameters
beta <- c(-1, 0.3, 3)

## Simulate idependent variables
n <- 900
AADT <- c(runif(n, min = 2000, max = 150000))
nlanes <- sample(x = c(2, 3, 4), size = n, replace = TRUE)
LNAADT <- log(AADT)

## Simulate dependent variable
theta <- exp(beta[1] + beta[2] * LNAADT + beta[3] * nlanes)
y <- rpois(n, theta)

## Fit model
mod <- glm(y ~ LNAADT + nlanes, family = poisson)

## Calculate residuals
res <- residuals(mod, type = "response")

## Calculate CURE plot data
cure_df <- calculate_cure_dataframe(AADT, res)

head(cure_df)

## Providing CURE data frame
cure_plot(cure_df)

## Providing glm object
cure_plot(mod, "LNAADT")
```

## Example with Resampling

```{r resampling}
library(cureplots)

## Basic example

set.seed(2000)

## Define parameters.
beta <- c(-1, 0.3, 3)

## Simulate idependent variables
n <- 900
AADT <- c(runif(n, min = 2000, max = 150000))
nlanes <- sample(x = c(2, 3, 4), size = n, replace = TRUE)
LNAADT <- log(AADT)

## Simulate dependent variable
theta <- exp(beta[1] + beta[2] * LNAADT + beta[3] * nlanes)
y <- rpois(n, theta)

## Fit model
mod <- glm(y ~ LNAADT + nlanes, family = poisson)

## Calculate residuals
res <- residuals(mod, type = "response")

## Calculate CURE plot data
cure_df <- calculate_cure_dataframe(AADT, res)



cure_plot(cure_df, n_resamples = 3)

```

```{=html}
<!-- 
To do list 
1. dd 
2. ccc 
-->
```
