---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cureplots

<!-- badges: start -->
<!-- badges: end -->

Cumulative residual (CURE) plots assesses the goodness-of-fit of a covariate in a generalized linear regression model, usually a negative binomial regression or a Poisson regression. The package `cureplots` produces CURE plots for the requested variables produced with [`ggplot2`](https://ggplot2.tidyverse.org/), or a table to easily produce a customized plot with the desired package.

## Installation

You can install the development version of cureplots from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gbasulto/cureplots")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(cureplots)

## basic example

set.seed(2000)

## Define parameters
beta <- c(-1, 0.3, 3)

## Simulate idependent variables
n <- 900
AADT <- c(runif(n, min = 2000, max = 150000))
nlanes <- sample(x = c(2, 3, 4), size = n, replace = TRUE)
LNAADT <- log(AADT)

## Simulate dependent variable
theta <- exp(beta[1] + beta[2] * LNAADT + beta[3] * nlanes)
y <- rpois(n, theta)

## Fit model
mod <- glm(y ~ LNAADT + nlanes, family = poisson)

## Calculate residuals
res <- residuals(mod)

## Calculate CURE plot data
cure_df <- calculate_cure_dataframe(AADT, res)

head(cure_df)

## Providing CURE data frame
cure_plot(cure_df)

## Providing glm object
cure_plot(mod, "LNAADT")
```


<!-- 
To do list 
1. dd 
2. ccc 
-->

